---
title: "Project1-hj2524_data_processing"
author: "Hanbo JIAO"
date: "2020/1/30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


In this R notebook, we will process more on processed lyrics for our data analysis.

### Step 0 - Load all the required libraries

From the packages' descriptions:

+ `tm` is a framework for text mining applications within R;
+ `data.table` is a package for fast aggregation of large data;
+ `tidyverse` is an opinionated collection of R packages designed for data science. All packages share an underlying design philosophy, grammar, and data structures;
+ `tidytext` allows text mining using 'dplyr', 'ggplot2', and other tidy tools;
+ `DT` provides an R interface to the JavaScript library DataTables.
+ `wordcloud` is a package for plot wordcloud of data.
+ `RColorBrewer` 
+ `reshape2`

```{r load libraries, warning=FALSE, message=FALSE}
packages.used=c("tm", "tidytext","tidyverse","DT","wordcloud","data.table","RColorBrewer","reshape2")

# check packages that need to be installed.
packages.needed=setdiff(packages.used, 
                        intersect(installed.packages()[,1], 
                                  packages.used))

# install additional packages
if(length(packages.needed)>0){
  install.packages(packages.needed, dependencies = TRUE)
}

# load packages
library(tm)
library(data.table)
library(tidytext)
library(tidyverse)
library(DT)
library(wordcloud)
library(RColorBrewer)
library(reshape2)

source("../lib/function_defined.R")
```

### Step 1 - Load the data to be cleaned and processed
```{r}
# load lyrics data from Text_processed
load('../output/processed_lyrics.RData')

# load artists information
artists <- read_csv("~/GitHub/Spring2020-Project1-hj2524/data/artists.csv")
```

### Step 2 - Determine whether artist is team or individual
```{r}
# find a list of team artist
team_list<-artists%>%select(-Intro,-Origin)%>%filter(!is.na(Formed)|!is.na(Members))%>%filter(is.na(Formed)|!Formed==199)%>%pull(Artist)

# add a column that indicates team or individual  
data<-dt_lyrics%>%mutate(team=artist%in%team_list)%>%filter(year>1000)
```

### Step 3 - Filter out Pop music only and Export data
```{r}
# Filter out Pop music
data_Pop<-data%>%filter(genre%in% c("Pop"))

# Export data
save(data_Pop, file="../output/data_Pop.RData")

```

### Step 4 - Count the frequent of positive & negative words in lyrics of Pop music based on sentiment "nrc" and Export data
```{r}
# import sentiment nrc
nrc <- get_sentiments("nrc") 

# combine sentiment with TDM of lyrics of pop music.
pop_nrc<-tdm(data_Pop)%>%inner_join(nrc,by=c("term"="word"))%>%rename("n"=`sum(count)`)

# Keep those positive and negative sentiments data.
pop_plot_sentiment<-pop_nrc %>%
  filter(sentiment%in%c("positive","negative"))%>%
  group_by(sentiment)

# Export data
save(pop_plot_sentiment, file="../output/pop_plot_sentiment.RData")
```

### Step 5 - For different types of music, determine different types of artists are positive or negative based on sentiment "bing" and Export data
```{r}
# import sentiment bing
bing<-get_sentiments("bing")

# For any artists among all types of music, 
# count the frequent of positive & negative words in lyrics of all of her songs,
# and find if there are more positive words or more negative words in all of her songs.
data_plot_sentiment<-
  data%>%group_by(genre,artist)%>%
  nest%>%mutate(tdm=map(data,tdm))%>%select(-data)%>%
  unnest(col=c("tdm"))%>%
  inner_join(bing,by=c("term"="word"))%>%rename("n"=`sum(count)`)%>%
  group_by(genre,artist,sentiment)%>%summarise(n=n())%>%
  spread(sentiment,n)%>%
  transmute(n=positive-negative)

# Export data
save(data_plot_sentiment, file="../output/data_plot_sentiment.RData")
```



```{r}
load("../output/processed_lyrics.RData")
source("../lib/function_defined.R")
#nrc<-nrc%>%rename(word=term)

eight_emotions_f<-function(x){
  tidy_lyrics%>%
    filter(genre==x)%>%
    semi_join(nrc)%>%
    count(word,sort=TRUE)%>%
    inner_join(nrc)%>%
    pivot_longer(cols=-c("word","n"),
               names_to = "emotions",values_to = "amount")%>%
  select(emotions,amount)%>%
  group_by(emotions)%>%mutate(n=sum(amount))%>%head(8)%>%select(emotions,n)
}


eight_emotions_f<-function(x){
  newname=x
  dt_lyrics%>%
    filter(genre==x)%>%tdm%>%rename(word=term)%>%
    inner_join(nrc)%>%
    rename(emotions=sentiment,amount=`sum(count)`)%>%
    select(emotions,amount)%>%
  group_by(emotions)%>%mutate(n=sum(amount))%>%head(8)%>%select(emotions,n)%>%rename(newname=emotions)
}


genre_name_select<-c("Pop","Indie")
eight_emotions_genre<-map(genre_name_select,eight_emotions_f)

eight_emotions_genre

#save(eight_emotions_genre, file="../output/1.RData")
#save(genre_name_select, file="../output/2.RData")
#save(nrc_emotions, file="../output/3.RData")
#save(tidy_lyrics, file="../output/4.RData")

for(i in seq_along(genre_name_select)){
names(eight_emotions_genre[[i]])<-c(genre_name_select[i],"n")
  }
```


